Effects of CHILDREN's programs

### 2020-02-25 paper.Rnw
dfghj

@@

texreg(list(lm_ms, lm_ts, lm_ms_o, lm_ts_o, lm_ms_i, lm_ts_i), caption = "Grants Regressions", custom.model.names = c("MealsNo", "Trips No", "Meals No", "Trips No", "Meals No", "Trips No"))
@
Table 3: The first two columns are simple OLS models, in column 3 and 4 outliers are excluded and in column 5 and 6 data is imputed.

@@

>>>>

\begin{equation}
\label{Equation 1}
  y_{it} = \beta_0 + \beta_1 x_{it} + \epsilon_{it}
\end{equation}

In this section we use a standard OLS equation, as described in equation 1. Where needed, we modified the given data, by using weights, excluding outliers and by scaling relevant variables. We also compared the results with the actual dataset to the results we gained by using a dataset in which we imputed necessary data. (DESCRIBE METHODS EXACT)

\\Number of Meals and Number of Trips

As the first variables of interest we consider the number of meals the organizations recorded and the number of trips the organizations made together with the beneficiaries. In this case, we use standard OLS in a first equation, exclude outliers from the variables 'mealsNo' and 'tripsNo' to obtain a believable value and compare to the imputed dataset. TableX shows the regression results.

@@

texreg(list(lm_ms, lm_ts, lm_ms_o, lm_ts_o, lm_ms_i, lm_ts_i), caption = "Grants Regressions", custom.model.names = c("MealsNo", "Trips No", "Meals No", "Trips No", "Meals No", "Trips No"))
@
The first two columns are simple OLS models, in column 3 and 4 outliers are excluded and in column 5 and 6 data is imputed. 
(DESCRIBE RESULTS) (COMPARE TO SUMMARY STATISTICS)

In the next section, we want to explore the influence of the DGE Criterion on relevant health outcomes.

@@

In the following equation we use standardized variables in a standard OLS approach. The results are as well compared to the output with the imputed dataset, where we also use scaled coefficents.

### 2020-02-25 paper.tex
dfghj

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Tue Feb 25 23:58:46 2020
\begin{table}[ht]
\centering
\begin{tabular}{mmmmm}
  \hline
Year & Beneficiaries, Meals & Beneficiaries, Trips & Organizations, Meals & Organizations, Trips \\ 
  \hline
2011 & 3748.0 &  & 52 &  \\ 
  2012 & 3556.0 & 2803.0 & 51 & 44 \\ 
  2013 & 4015.0 & 2823.0 & 55 & 42 \\ 
  2014 & 4685.0 & 2752.0 & 55 & 43 \\ 
  2015 & 5857.0 & 3823.0 & 55 & 49 \\ 
  2016 & 3075.0 & 3819.0 & 59 & 48 \\ 
  2017 & 4895.0 & 4150.0 & 64 & 48 \\ 
  2018 & 5102.5 & 6911.0 & 68 & 49 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{l c c c c c c }
\hline
 & MealsNo & Trips No & Meals No & Trips No & Meals No & Trips No \\
\hline
(Intercept)      & $-12089.14^{*}$ & $3.70^{***}$ & $-12089.14^{***}$ & $3.70^{***}$ & $-12250.60^{***}$ & $3.62^{***}$ \\
                 & $(5192.86)$     & $(0.33)$     & $(2919.15)$       & $(0.25)$     & $(2500.33)$       & $(0.25)$     \\
realSubsidy      & $2.61^{***}$    &              & $2.61^{***}$      &              & $2.72^{***}$      &              \\
                 & $(0.57)$        &              & $(0.17)$          &              & $(0.14)$          &              \\
realTripsSubsidy &                 & $0.00^{*}$   &                   & $0.00^{***}$ &                   & $0.00^{***}$ \\
                 &                 & $(0.00)$     &                   & $(0.00)$     &                   & $(0.00)$     \\
\hline
R$^2$            & 0.43            & 0.05         & 0.43              & 0.05         & 0.45              & 0.05         \\
Adj. R$^2$       & 0.43            & 0.04         & 0.43              & 0.04         & 0.45              & 0.05         \\
Num. obs.        & 329             & 322          & 329               & 322          & 440               & 334          \\
RMSE             & 39992.79        & 2.96         & 39992.79          & 2.96         & 39601.41          & 2.93         \\
\hline
\multicolumn{7}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
\caption{Grants Regressions}
\label{table:coefficients}
\end{center}
\end{table}

Table 3: The first two columns are simple OLS models, in column 3 and 4 outliers are excluded and in column 5 and 6 data is imputed.

@@

{\ttfamily\noindent\color{warningcolor}{\#\# Warning in gzfile(file, "{}rb"{}): cannot open compressed file './ANALYSIS/Tables/Expand\_LessIll\_IM\_scaled.Rds', probable reason 'No such file or directory'}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): cannot open the connection}}\end{kframe}
\begin{table}
\begin{center}
\begin{tabular}{l c c c c c c }
\hline
 & LessIll & DietaryKnowledge & AppreciateHealthy & LessIll & DietaryKnowledge & AppreciateHealthy \\
\hline
(Intercept)         & $0.02$       & $0.02$   & $-0.03$      & $0.09$       & $0.02$     & $0.02$       \\
                    & $(0.08)$     & $(0.07)$ & $(0.07)$     & $(0.07)$     & $(0.06)$   & $(0.06)$     \\
DGECriteriaNoScaled & $0.33^{***}$ & $0.11$   & $0.27^{***}$ & $0.25^{***}$ & $0.12^{*}$ & $0.25^{***}$ \\
                    & $(0.08)$     & $(0.07)$ & $(0.07)$     & $(0.07)$     & $(0.06)$   & $(0.06)$     \\
\hline
R$^2$               & 0.12         & 0.01     & 0.06         & 0.07         & 0.02       & 0.06         \\
Adj. R$^2$          & 0.11         & 0.01     & 0.06         & 0.07         & 0.01       & 0.06         \\
Num. obs.           & 121          & 214      & 213          & 177          & 275        & 274          \\
RMSE                & 0.91         & 0.98     & 1.02         & 0.94         & 0.96       & 1.01         \\
\hline
\multicolumn{7}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
\caption{Health Outcome Regressions}
\label{table:coefficients}
\end{center}
\end{table}

@@

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in l[[i]]: subscript out of bounds}}\end{kframe}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Tue, Feb 25, 2020 - 11:58:54 PM
% Requires LaTeX packages: dcolumn rotating 
\begin{sidewaystable}[!htbp] \centering 
  \caption{Regression Results} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
\hline \\[-1.8ex] 
 Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
  & (0.065) & (0.095) & (0.092) & (0.107) \\ 
  & & & & \\ 
 treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
  & (0.074) & (0.097) & (0.075) & (0.100) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
ID fixed effects & No & No & Yes & Yes \\ 
Time fixed effects & No & Yes & No & Yes \\ 
Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{sidewaystable}

@@

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Tue Feb 25 23:58:54 2020
\begin{table}[ht]
\centering
\begin{tabular}{rllr}
  \hline
 & Variable, Meals & Mapping, Meals & Information, Meals \\ 
  \hline
1 & participateMore & participateMore & 1.00 \\ 
  2 & tasksLunch & tasksLunch & 1.00 \\ 
  3 & ownIdeas & ownIdeas & 1.00 \\ 
  4 & stayLonger & stayLonger & 1.00 \\ 
  5 & dietaryKnowledge & dietaryKnowledge & 1.00 \\ 
  6 & appreciateHealthy & appreciateHealthy & 1.00 \\ 
  7 & foodCulture & foodCulture & 1.00 \\ 
  8 & lessIll & lessIll & 1.00 \\ 
  9 & betterTeamwork & betterTeamwork & 1.00 \\ 
  10 & moreRegularSchoolVisits & moreRegularSchoolVisits & 1.00 \\ 
  11 & addressProblems & addressProblems & 1.00 \\ 
  12 & reduced\_var\_1 & moreConcentrated & 0.66 \\ 
  13 & reduced\_var\_1 & moreBalanced & 0.66 \\ 
  14 & reduced\_var\_2 & monthlyCooks & 0.42 \\ 
  15 & reduced\_var\_2 & weeklyCooks & 0.42 \\ 
  16 & reduced\_var\_2 & shoppers & 0.42 \\ 
  17 & reduced\_var\_2 & easyDishes & 0.42 \\ 
  18 & reduced\_var\_3 & dayToDaySkills & 0.43 \\ 
  19 & reduced\_var\_3 & moreIndependent & 0.43 \\ 
  20 & reduced\_var\_3 & selfworth & 0.43 \\ 
  21 & reduced\_var\_3 & moreOpen & 0.43 \\ 
  22 & reduced\_var\_3 & moreConfidence & 0.43 \\ 
  23 & reduced\_var\_3 & proud & 0.43 \\ 
  24 & reduced\_var\_4 & betterReading & 0.53 \\ 
  25 & reduced\_var\_4 & betterNumbers & 0.53 \\ 
  26 & reduced\_var\_4 & betterGrades & 0.53 \\ 
  27 & reduced\_var\_5 & influenceHome & 0.41 \\ 
  28 & reduced\_var\_5 & cookAtHome & 0.41 \\ 
  29 & reduced\_var\_5 & askRecipes & 0.41 \\ 
   \hline
\end{tabular}
\caption{Partition of outcomes, Meals} 
\end{table}
% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Tue Feb 25 23:58:54 2020
\begin{table}[ht]
\centering
\begin{tabular}{rllr}
  \hline
 & Variable, Trips & Mapping, Trips & Information, Trips \\ 
  \hline
1 & tripsSuggestions & tripsSuggestions & 1.00 \\ 
  2 & tripsDecisions & tripsDecisions & 1.00 \\ 
  3 & tripsOrganization & tripsOrganization & 1.00 \\ 
  4 & tripsCostCalculation & tripsCostCalculation & 1.00 \\ 
  5 & tripsBudget & tripsBudget & 1.00 \\ 
  6 & tripsMoney & tripsMoney & 1.00 \\ 
  7 & tripsReview & tripsReview & 1.00 \\ 
  8 & tripsPublicTransport & tripsPublicTransport & 1.00 \\ 
  9 & tripsMobility & tripsMobility & 1.00 \\ 
  10 & tripsAdditionalActivities & tripsAdditionalActivities & 1.00 \\ 
  11 & tripsSelfworth & tripsSelfworth & 1.00 \\ 
  12 & tripsFrustrationTolerance & tripsFrustrationTolerance & 1.00 \\ 
  13 & reduced\_var\_1 & tripsSuccess & 0.68 \\ 
  14 & reduced\_var\_1 & tripsSelfEfficacy & 0.68 \\ 
  15 & reduced\_var\_2 & tripsNewPlaces & 0.60 \\ 
  16 & reduced\_var\_2 & tripsNewCommunities & 0.60 \\ 
  17 & reduced\_var\_2 & tripsNewIdeas & 0.60 \\ 
  18 & reduced\_var\_2 & tripsSocialSkills & 0.60 \\ 
  19 & reduced\_var\_3 & tripsSpecificSkills & 0.46 \\ 
  20 & reduced\_var\_3 & tripsDayToDaySkills & 0.46 \\ 
   \hline
\end{tabular}
\caption{Partition of outcomes, Trips} 
\end{table}
\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right, max = max): invalid 'digits' argument}}\end{kframe}

>>>>

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Wed Feb 26 00:35:31 2020
\begin{table}[ht]
\centering
\begin{tabular}{mmmmm}
  \hline
Year & Beneficiaries, Meals & Beneficiaries, Trips & Organizations, Meals & Organizations, Trips \\ 
  \hline
2011 & 3748.0 &  & 52 &  \\ 
  2012 & 3556.0 & 2803.0 & 51 & 44 \\ 
  2013 & 4015.0 & 2823.0 & 55 & 42 \\ 
  2014 & 4685.0 & 2752.0 & 55 & 43 \\ 
  2015 & 5857.0 & 3823.0 & 55 & 49 \\ 
  2016 & 3075.0 & 3819.0 & 59 & 48 \\ 
  2017 & 4895.0 & 4150.0 & 64 & 48 \\ 
  2018 & 5102.5 & 6911.0 & 68 & 49 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\end{table}

@@

\begin{equation}
\label{Equation 1}
  y_{it} = \beta_0 + \beta_1 x_{it} + \epsilon_{it}
\end{equation}

In this section we use a standard OLS equation, as described in equation 1. Where needed, we modified the given data, by using weights, excluding outliers and by scaling relevant variables. We also compared the results with the actual dataset to the results we gained by using a dataset in which we imputed necessary data. (DESCRIBE METHODS EXACT)

\\Number of Meals and Number of Trips

As the first variables of interest we consider the number of meals the organizations recorded and the number of trips the organizations made together with the beneficiaries. In this case, we use standard OLS in a first equation, exclude outliers from the variables 'mealsNo' and 'tripsNo' to obtain a believable value and compare to the imputed dataset. TableX shows the regression results.

\begin{table}
\begin{center}
\begin{tabular}{l c c c c c c }
\hline
 & MealsNo & Trips No & Meals No & Trips No & Meals No & Trips No \\
\hline
(Intercept)      & $-12089.14^{*}$ & $3.70^{***}$ & $-12089.14^{*}$ & $3.70^{***}$ & $-12250.60^{**}$ & $3.62^{***}$ \\
                 & $(5192.86)$     & $(0.33)$     & $(5192.86)$     & $(0.33)$     & $(4524.09)$      & $(0.33)$     \\
realSubsidy      & $2.61^{***}$    &              & $2.61^{***}$    &              & $2.72^{***}$     &              \\
                 & $(0.57)$        &              & $(0.57)$        &              & $(0.51)$         &              \\
realTripsSubsidy &                 & $0.00^{*}$   &                 & $0.00^{*}$   &                  & $0.00^{*}$   \\
                 &                 & $(0.00)$     &                 & $(0.00)$     &                  & $(0.00)$     \\
\hline
R$^2$            & 0.43            & 0.05         & 0.43            & 0.05         & 0.45             & 0.05         \\
Adj. R$^2$       & 0.43            & 0.04         & 0.43            & 0.04         & 0.45             & 0.05         \\
Num. obs.        & 329             & 322          & 329             & 322          & 440              & 334          \\
RMSE             & 39992.79        & 2.96         & 39992.79        & 2.96         & 39601.41         & 2.93         \\
\hline
\multicolumn{7}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
\caption{Grants Regressions}
\label{table:coefficients}
\end{center}
\end{table}

The first two columns are simple OLS models, in column 3 and 4 outliers are excluded and in column 5 and 6 data is imputed. 
(DESCRIBE RESULTS) (COMPARE TO SUMMARY STATISTICS)

In the next section, we want to explore the influence of the DGE Criterion on relevant health outcomes.

@@

{\ttfamily\noindent\color{warningcolor}{\#\# Warning in gzfile(file, "{}rb"{}): kann komprimierte Datei './ANALYSIS/Tables/Expand\_LessIll\_IM\_scaled.Rds' nicht öffnen. Grund evtl. 'No such file or directory'}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): kann Verbindung nicht öffnen}}\end{kframe}
\begin{table}
\begin{center}
\begin{tabular}{l c c c c c c }
\hline
 & LessIll & DietaryKnowledge & AppreciateHealthy & LessIll & DietaryKnowledge & AppreciateHealthy \\
\hline
(Intercept)         & $0.02$       & $0.02$   & $-0.03$      & $0.09$       & $0.02$     & $0.02$       \\
                    & $(0.08)$     & $(0.07)$ & $(0.07)$     & $(0.07)$     & $(0.06)$   & $(0.06)$     \\
DGECriteriaNoScaled & $0.33^{***}$ & $0.11$   & $0.27^{***}$ & $0.25^{***}$ & $0.12^{*}$ & $0.25^{***}$ \\
                    & $(0.08)$     & $(0.06)$ & $(0.07)$     & $(0.07)$     & $(0.05)$   & $(0.06)$     \\
\hline
R$^2$               & 0.12         & 0.01     & 0.06         & 0.07         & 0.02       & 0.06         \\
Adj. R$^2$          & 0.11         & 0.01     & 0.06         & 0.07         & 0.01       & 0.06         \\
Num. obs.           & 121          & 214      & 213          & 177          & 275        & 274          \\
RMSE                & 0.91         & 0.98     & 1.02         & 0.94         & 0.96       & 1.01         \\
\hline
\multicolumn{7}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
\end{tabular}
\caption{Health Outcome Regressions}
\label{table:coefficients}
\end{center}
\end{table}

@@

{\ttfamily\noindent\color{warningcolor}{\#\# Warning in gzfile(file, "{}rb"{}): kann komprimierte Datei './ANALYSIS/Tables/selfworthTrips\_scaled.lm.Rds' nicht öffnen. Grund evtl. 'No such file or directory'}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): kann Verbindung nicht öffnen}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in "{}list"{} \%in\% class(l)[1]: Objekt 'tss' nicht gefunden}}\end{kframe}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning in gzfile(file, "{}rb"{}): kann komprimierte Datei './ANALYSIS/Tables/selfworth\_IM\_scaled.Rds' nicht öffnen. Grund evtl. 'No such file or directory'}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): kann Verbindung nicht öffnen}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in "{}list"{} \%in\% class(l)[1]: Objekt 'ssI' nicht gefunden}}\end{kframe}

@@

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Mi, Feb 26, 2020 - 00:35:36
% Requires LaTeX packages: dcolumn rotating 
\begin{sidewaystable}[!htbp] \centering 
  \caption{Regression Results} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
\cline{2-5} 
\\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
\hline \\[-1.8ex] 
 Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
  & (0.065) & (0.095) & (0.092) & (0.107) \\ 
  & & & & \\ 
 treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
  & (0.074) & (0.097) & (0.075) & (0.100) \\ 
  & & & & \\ 
\hline \\[-1.8ex] 
ID fixed effects & No & No & Yes & Yes \\ 
Time fixed effects & No & Yes & No & Yes \\ 
Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{sidewaystable}

@@

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Wed Feb 26 00:35:36 2020
\begin{table}[ht]
\centering
\begin{tabular}{rllr}
  \hline
 & Variable, Meals & Mapping, Meals & Information, Meals \\ 
  \hline
1 & participateMore & participateMore & 1.00 \\ 
  2 & tasksLunch & tasksLunch & 1.00 \\ 
  3 & ownIdeas & ownIdeas & 1.00 \\ 
  4 & stayLonger & stayLonger & 1.00 \\ 
  5 & dietaryKnowledge & dietaryKnowledge & 1.00 \\ 
  6 & appreciateHealthy & appreciateHealthy & 1.00 \\ 
  7 & foodCulture & foodCulture & 1.00 \\ 
  8 & lessIll & lessIll & 1.00 \\ 
  9 & betterTeamwork & betterTeamwork & 1.00 \\ 
  10 & moreRegularSchoolVisits & moreRegularSchoolVisits & 1.00 \\ 
  11 & addressProblems & addressProblems & 1.00 \\ 
  12 & reduced\_var\_1 & moreConcentrated & 0.66 \\ 
  13 & reduced\_var\_1 & moreBalanced & 0.66 \\ 
  14 & reduced\_var\_2 & monthlyCooks & 0.42 \\ 
  15 & reduced\_var\_2 & weeklyCooks & 0.42 \\ 
  16 & reduced\_var\_2 & shoppers & 0.42 \\ 
  17 & reduced\_var\_2 & easyDishes & 0.42 \\ 
  18 & reduced\_var\_3 & dayToDaySkills & 0.43 \\ 
  19 & reduced\_var\_3 & moreIndependent & 0.43 \\ 
  20 & reduced\_var\_3 & selfworth & 0.43 \\ 
  21 & reduced\_var\_3 & moreOpen & 0.43 \\ 
  22 & reduced\_var\_3 & moreConfidence & 0.43 \\ 
  23 & reduced\_var\_3 & proud & 0.43 \\ 
  24 & reduced\_var\_4 & betterReading & 0.53 \\ 
  25 & reduced\_var\_4 & betterNumbers & 0.53 \\ 
  26 & reduced\_var\_4 & betterGrades & 0.53 \\ 
  27 & reduced\_var\_5 & influenceHome & 0.41 \\ 
  28 & reduced\_var\_5 & cookAtHome & 0.41 \\ 
  29 & reduced\_var\_5 & askRecipes & 0.41 \\ 
   \hline
\end{tabular}
\caption{Partition of outcomes, Meals} 
\end{table}
% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Wed Feb 26 00:35:36 2020
\begin{table}[ht]
\centering
\begin{tabular}{rllr}
  \hline
 & Variable, Trips & Mapping, Trips & Information, Trips \\ 
  \hline
1 & tripsSuggestions & tripsSuggestions & 1.00 \\ 
  2 & tripsDecisions & tripsDecisions & 1.00 \\ 
  3 & tripsOrganization & tripsOrganization & 1.00 \\ 
  4 & tripsCostCalculation & tripsCostCalculation & 1.00 \\ 
  5 & tripsBudget & tripsBudget & 1.00 \\ 
  6 & tripsMoney & tripsMoney & 1.00 \\ 
  7 & tripsReview & tripsReview & 1.00 \\ 
  8 & tripsPublicTransport & tripsPublicTransport & 1.00 \\ 
  9 & tripsMobility & tripsMobility & 1.00 \\ 
  10 & tripsAdditionalActivities & tripsAdditionalActivities & 1.00 \\ 
  11 & tripsSelfworth & tripsSelfworth & 1.00 \\ 
  12 & tripsFrustrationTolerance & tripsFrustrationTolerance & 1.00 \\ 
  13 & reduced\_var\_1 & tripsSuccess & 0.68 \\ 
  14 & reduced\_var\_1 & tripsSelfEfficacy & 0.68 \\ 
  15 & reduced\_var\_2 & tripsNewPlaces & 0.60 \\ 
  16 & reduced\_var\_2 & tripsNewCommunities & 0.60 \\ 
  17 & reduced\_var\_2 & tripsNewIdeas & 0.60 \\ 
  18 & reduced\_var\_2 & tripsSocialSkills & 0.60 \\ 
  19 & reduced\_var\_3 & tripsSpecificSkills & 0.46 \\ 
  20 & reduced\_var\_3 & tripsDayToDaySkills & 0.46 \\ 
   \hline
\end{tabular}
\caption{Partition of outcomes, Trips} 
\end{table}
\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right, max = max): ungültiges 'digits' Argument}}\end{kframe}
